---
title: "Introduction_OralMicrobiomeSubstanceUse"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_OralMicrobiomeSubstanceUse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(OralMicrobiomeSubstanceUse)
```


## Introduction

`OralMicrobiomeSubstanceUse` is an R package developed to help with the analysis of oral microbial species found in substance users oral microbiome and to map the different kinds of microbial species found between different substances.

This package can help with mapping the common microbial species found in the oral microbiome to different types of substance use and can be used to come up with a comphrensive list of oral microbial species found in the oral microbiome of those who partake in substance use, to compare the different substances and to compare with non-users.

To download **OralMicrobiomeSubstanceUse**, following the commands:

``` r
require("devtools")
devtools::install_github("Maryam-hkiabi/OralMicrobiomeSubstanceUse", build_vignettes = TRUE)
library("OralMicrobiomeSubstanceUse")
```
List of all sample functions available in this package:
``` r
ls("package:OralMicrobiomeSubstanceUse")
```

List of the sample dataset available in this package:
``` r
data(package = "OralMicrobiomeSubstanceUse")
```

<br>

## Components


















